prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-19 inst/MyArticle/paper.Rmd
delta

When computing differences $\Delta$ among two groups $a$ and $b$, we will use the group mean $\bar{a}$ or $\bar{b}$ estimated from the data, or if no observations are present in a group we use $A_{LOD}$, e.g., If there are no observations in group $b$ then

>>>>

When computing differences $\Delta$ among two groups $a$ and $b$, we will use the group mean $\bar{a}$ or $\bar{b}$ estimated from the data, or if no observations are present in a group we use $A_{LOD}$, e.g., If there are no observations in group $b$ then :
